---
title: "Reproducible Pitch Presentation"
author: "A. Rodríguez"
date: "13/12/2020"
output: ioslides_presentation
---

## Previous projects featuring the dataset

### Statistical Inference Week 4 Assignment (Part 2)  

- Can be checked here: 
[Tooth growth analysis](https://coursera-assessments.s3.amazonaws.com/assessments/1600715936181/e1571097-8fd5-4162-8c44-b294cc4d74b7/Part%202%20-%20Basic-Inferential-Data-Analysis.pdf).



### Developing Data Products Week 4 Assignment (Shiny Application)
- Link to github repository:
[CourseApp](https://github.com/alroru95/Developing-data-products/tree/main/CourseApp).


## Dataset Details

### The Effect of Vitamin C on Tooth Growth in Guinea Pigs

- Description: The response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs. Each animal received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day) by one of two delivery methods, orange juice or ascorbic acid (a form of vitamin C and coded as VC).

- Format: A data frame with 60 observations on 3 variables.


- Source: C. I. Bliss (1952). The Statistics of Bioassay. Academic Press.

- References: McNeil, D. R. (1977). Interactive Data Analysis. New York: Wiley. //
Crampton, E. W. (1947). The growth of the odontoblast of the incisor teeth as a criterion of vitamin C intake of the guinea pig. The Journal of Nutrition, 33(5), 491–504. doi: 10.1093/jn/33.5.491.

## First glimpse of dataset

```{r dataset}
head(ToothGrowth)
```

- [,1]	len	(numeric): Tooth length.
- [,2]	supp (factor): Supplement type (VC or OJ).
- [,3]	dose (numeric):	Dose in milligrams/day



## Embedded R Code (Boxplot and fit model)

```{r server, message=FALSE}
library(shiny); library(datasets); library(ggpubr)
toothData <- ToothGrowth
shinyServer(function(input, output) {
    formulaTextPoint <- reactive
    ({paste("len ~", "as.integer(", input$variable, ")")})
    fit <- reactive
    ({lm(as.formula(formulaTextPoint()), data=toothData)})
    output$toothBoxPlot <- renderPlot
    ({boxplot(as.formula(formulaText()), data = toothData)})
    output$fit <- renderPrint({summary(fit())})
    output$toothPlot <- renderPlot({with(toothData, {
            plot(as.formula(formulaTextPoint()))
            abline(fit(), col=2)})
    })
})
```
